intro

### 2021-10-15 06_Paper/ER-ED/intro.Rmd
added comment
added comments

[...]
<!-- SVs wären gut um um besser sachen ausrechnen zu können-->
Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

@@

## 1.2 The present study
The aim of the present study is to evaluate, if this paradigm is suitable for determining SVs of ER strategies. 
We also want to find out whether the SVs are associated with subjective and physiological ER success, subjective effort, ER choice, and relevant personality traits.
We expect that (1) distancing and distraction lead to higher decrease in emotional arousal (subjective ratings, corrugator and levator activity) than suppression, (2a) people select the ER strategy that is less effortful if they have a choice, (2b) distancing is subjectively effortful than distraction and suppression.
Regarding SVs of ER strategies we expect that (3a) people chose to re-apply the strategy with the highest SV, (3b) SVs of strategies are predicted by subjective arousal and levator and corrugator activity and subjective effort.
Regarding personality traits, we expect that (4a) self-regulation is associated with ER success and (4b) people with higher ER flexibility show no clearly preferred strategy in SVs.

>>>>

[...]
Associations between subjectively reported habitual use of emotion regulation strategies <!-- Als Überleitung: Maladaptive ER Strategien zu ER Flexibility -->  
ER flexibility has been described as an approach to 
[...]
<!-- Überleitung zu SVs-->
Individual subjective values (SV) of cognitive effort have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

@@

## 1.2 The present study
The aim of the present study is to evaluate, if this paradigm is suitable for determining SVs of ER strategies. 
We also want to find out whether the SVs are associated with subjective and physiological ER success, subjective effort, ER choice, and relevant personality traits.
We expect that (1) distancing and distraction lead to higher decrease in emotional arousal (subjective ratings, corrugator and levator activity) than suppression, (2a) people select the ER strategy that is less effortful if they have a choice, (2b) distancing is subjectively effortful than distraction and suppression.
Regarding SVs of ER strategies we expect that (3a) people chose to re-apply the strategy with the highest SV, (3b) SVs of strategies are predicted by subjective arousal and levator and corrugator activity and subjective effort.
Regarding personality traits, we expect that (4a) self-regulation is associated with ER success and (4b) people with higher ER flexibility show no clearly preferred strategy in SVs. 
<!-- to specific ? to unspecific? -->
